A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-03 doc/draft-01-stokes/04numerical.tex
update numerical section, add barbell driver

Once the discretization is set, we can form
a compressed representation of the system matrix
using recursive skeletonization~\cite{ho2012fast}.
%
We use the recursive skeletonization algorithm
included in the fast linear algebra in
MATLAB (\texttt{FLAM}) package by
Kenneth Ho~\cite{hoFLAM_1253582}.
%
At low-to-medium frequencies, the scaling
of the recursive skeletonization algorithm
is $O(N\log N)$ in operation count and
storage and allows for a fast determinant
calculation in $O(N\log N)$ time as a
follow-up step, by using a generalization
of the Sylvester determinant formula.
%
At higher-frequencies,
the recursive skeletonization procedure,
which is based on the assumption that off-diagonal
blocks of the matrix are of low rank,
breaks down and does not offer a speed advantage.
%
These algorithms take a precision parameter
$\epsflam$ which determines the
accuracy to which any sub-blocks of the matrix
should be compressed. In all experiments,
we set $\epsflam = 10^{-14}$.

>>>>

Once the discretization is set, we can form
a compressed representation of the system matrix
using recursive skeletonization~\cite{ho2012fast}.
%
We use the implementation of this procedure
included in the fast linear algebra in
MATLAB (\texttt{FLAM}) package
\cite{hoFLAM_1253582}.
%
At low-to-medium frequencies, the scaling
of the recursive skeletonization algorithm
is $O(N\log N)$ in operation count and
storage and, by using a generalization
of the Sylvester determinant formula,
allows for a fast determinant
calculation in $O(N\log N)$ time as a
follow-up step.
%
At higher-frequencies,
the recursive skeletonization procedure,
which is based on the assumption that off-diagonal
blocks of the matrix are of low rank,
breaks down and does not offer a speed advantage.
%
These algorithms take a precision parameter
$\epsflam$ which determines the
accuracy to which any sub-blocks of the matrix
should be compressed. In all experiments,
we set $\epsflam = 10^{-14}$.
